\documentclass{article}
\begin{document}

\title{A RESEARCH REPORT ON BULLYING AND HOW I WOULD OVERCOME IT IN SCHOOL.}
\author{NANTALE MARY VIVIAN        15/U/10829/PS      215013868 }
\maketitle
\tableofcontents
\subsection{INTRODUCTION }{Before joining primary level when I was a child, my elder siblings always told me to watch out for other children, more so elder ones that would dare take a chance of taking advantage of me through bullying. It was also to advantage for me that we were in the same school, them being in higher classes. So I always had who to run to first in case I sensed any form of bullying towards me.}
\subsection{WHAT IS BULLYING?}{Bullying is mostly about gaining strength, being the boss, scaring pupils and sometimes hurting them. Pupils would be bullied by being threatened ,not having friends because of their race or even  being called bad names more so nicknames associated with something that is not nice and their physical appearance.
Earlier in school during my studies, we identified four types of bullying; physical bullying, verbal, convert and cyber bullying. Physical bullying involves pinching, kicking, tripping, hitting or kicking a fellow person, or even damaging property. Verbal bullying includes name calling, insults, teasing, intimidation, homophobic or racist marks or verbal abuse. Convert bullying is often harder to recognize and can be carried out behind the bullied persons back. It is designed to harm someone’s social relationship with fellow friends. Cyber bullying is defined as an aggressive, intentional act carried out by a group 0f people or individual, using electronic forms of conduct repeatedly or over time against a victim who cannot easily defend him or herself. This is a very bad form of bullying and it is causing many problems for many teens and their families and their loved ones. This is because kids have killed each other and even committed suicide after being involved in cyber bullying. 
There are also incidences of bullying in public places such as parks and recreation centers where children socialize with each other. In this digital age (commonly referred to as the dot com era) bullying can move across physical boundaries and even permeates social networking sites through the internet such as Facebook, Whatsapp and Twitter.
}
\subsection{ OUTCOMES}{ If a pupil is bullied, she or he would feel depressed and not so good about themselves, fail in school and also try to commit suicide (this being an incidence that we would hear from other schools) I always felt like some kids who bully should be punished severely because it always hurt me so much seeing someone hurt emotionally, considering most of my friends who had weak feelings. Pupils who would see fellow pupils bullying would be afraid to tell, in fear of being bullied too incase they report. 
Other pupils who are bullied often suffer from repeated trauma. They become timid and exhibit an inferiority complex which can aggravate to the extent it can affect their future, in their academics, social circles or could lead to suicide.
}
\subsection{HOW TO OVERCOME}{If I were to be bullied, I would not feel like going to school anymore, I may not want to learn or I may hate myself. In addition to telling my siblings, I would also tell my parents about it, seeking for comfort and how to overcome such situations.
Bullying is a serious issue that should be addressed in our society immediately. I also think that pupils who are bullied should tell a grownup that they trust before it’s too late. Schools and parents should also should work together to tackle the issue. They have to be keen on this issue since they handle the formative development of the children. Most cases of bullying start inside school. Teachers, administrators and also fellow students that are leaders can intervene support and educate students about ending bullying behaviors directly and indirectly, breaking the bullying circle. 
}
\subsection{CONCLUSION }{Parents and elders should not let children feel like they cannot overcome bullying. I wish that everyone can be nice and stop the bullying in schools so we can concentrate on our studies and attain good grades.                                       }
\end{document}